Digital Analysis of Paintings

### 2014-04-29 paper.tex
More a good stab at a few of the papers.

\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  \graphicspath{{../img/}}
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  \usepackage[dvips]{graphicx}
  \graphicspath{{../img/}}
  \DeclareGraphicsExtensions{.eps}
\fi

@@

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

@@

@@

>>>>

\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  \graphicspath{{img/}}
  \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  \usepackage[dvips]{graphicx}
  \graphicspath{{../img/}}
  \DeclareGraphicsExtensions{.eps}
\fi

@@

% *** SUBFIGURE PACKAGES ***
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

@@

For techniques which involve applying a filter to decide the direction of a
line within a picture, one often needs to be able to change or rotate the
filter by varying amounts of degrees. This principal is often described as
steering a filter and an efficient technique for doing so is described in 
\cite{freeman91design} in both two and three dimensional space.

This technique involves finding a function of $x$ and $y$ which steers a filter

% TODO I'm struggling to understand this one...

@@

Another analysis paradigm is fractal geometry which is based on the idea that
all analysis performed on an image at difference scales are equally important
and that the richest information can be found in the mechanisms which relate
them to one another.

Because of this, fractal tools can be used to analyse contours and textures of
images.

Multifractal analysis concentrates on the use of processing tools which
describe the fluctuations within regular regions of an object which at
different scales.

Until recently multifractal analysis was rarely applied to image processing
problems, but with the breakthrough in an efficient formulation of
multifractal analysis obtained through wavelet leaders.

The use of wavelet leader multifractal analysis has been used to explore
painting texture classification\cite{abry2013van}.

Image processing is a field which has grown out of signal processing; an image
can actually be thought of as a two-dimensional signal, which allows existing
signal processing techniques to be applied to them. In early days of image
processing the Fourier transform was often used to decompose images into
signals. In more recent years wavelets and transforms using wavelets have
become more popular, as they can provide all the features of a Fourier
transform, but also provide localised time information, as well as localised
frequency information.

In the case of images, localised time information maps to the location within
an image.

In this research, a 2D discrete wavelet transform is applied to the image to
gather the wavelets coefficients, normalising the image to the correct form
needed for the definition of wavelet leaders.

These coefficients enable a definition of the global regularity of the image.

To allow image classification across different scales, one needs a dyadic
space; a space in which there are a collection of regions of different scales,
where a region at one scale can also be viewed as the union of regions in a
smaller scale. Figure~\ref{fig:dyadic-image} shows an example of this where the
large regions show only a pixalated view of the image and the smallest the
individual pixels of the image.

\begin{figure}[ht]
\centering
\subfloat[$C=8$]{\includegraphics[width=0.1\textwidth]{dyadic_2.png}}%
\hspace{.2in}%
\subfloat[$C=32$]{\includegraphics[width=0.1\textwidth]{dyadic_4.png}}%
\hspace{.2in}%
\subfloat[$C=128$]{\includegraphics[width=0.1\textwidth]{dyadic_8.png}}%
\hspace{.2in}%
\subfloat[$C=512$]{\includegraphics[width=0.1\textwidth]{dyadic_16.png}}%
\caption{Example of dyadic space using the standard Lenna image (512x512
pixels) at different dyadic scales ($C$), note how the picture becomes less
pixalated at higher scales}
\label{fig:dyadic-image}
\end{figure}
